PANCHANGE_analysis

### 2020-11-16 PANCHANGE_analysis.Rmd
education, employment & employment change sensitivity

---
title: "PANCHANGE_analysis"
author: "Katherine N Thompson, Christopher Hüebel, Molly R Davies, Kirstin L Purves"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output:
  html_document:
    df_print: paged
    toc: yes
    toc_depth: 2
    toc_float:
      collapsed: false
    number_sections: false
    highlight: monochrome
    theme: cerulean
code_folding: show

@@

```{r source file path}
#source data directory: data_path
source("../PANCHANGE_raw_path.R")

print(data_path)

```

@@

# GAD baseline, not controlling for prior symptoms
### Model 0a: Disorder_hierarchical, Unadjusted

#SB Hashing out this chunk of code as it is not included in our final analysis and is currently breaking the code.
```{r gad model0a absolute whole sample}
# Regression coefficients
gad_baseline_model0a_estimates <- model0a.estimates(outcome = "gad.sum_score_base",
                                                 data_set = "dat")
#kable(gad_baseline_model0a_estimates)
gad_baseline_model0a_estimates

# Regression diagnostic statistics
gad_baseline_model0a_reg_stats <- model0a.reg.stats(outcome = "gad.sum_score_base",
                                                 data_set = "dat")
#kable(gad_baseline_model0a_reg_stats)
gad_baseline_model0a_reg_stats
```

@@

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
```{r ocir model1b absolute whole sample}
# Regression coefficients
ocir_baseline_model1b_estimates <- model1b.estimates(outcome = "ocir.sum_score_base",
                                                 data_set = "dat")
kable(ocir_baseline_model1b_estimates)
ocir_baseline_model1b_estimates

@@

### Model 1a: Disorder hierarchical, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
```{r ocir model1a diff_score prepan}
# Regression coefficients
ocir_prepan_model1a_estimates <- model1a.estimates(outcome = "ocir.diff_score_base_prepan",
                  data_set = "dat.prepan")
kable(ocir_prepan_model1a_estimates)
ocir_prepan_model1a_estimates

@@

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
```{r ocir model1b diff_score prepan}
# Regression coefficients
ocir_prepan_model1b_estimates <- model1b.estimates(outcome = "ocir.diff_score_base_prepan",
                  data_set = "dat.prepan")
kable(ocir_prepan_model1b_estimates)
ocir_prepan_model1b_estimates

@@

### Model 1a: Disorder hierarchical, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
```{r ocir model1a sum_score prepan}
# Regression coefficients
ocir_prepan_model1a_explan_estimates <- model1a.explan.estimates(outcome = "ocir.sum_score_base",
                         explan_var = "ocir.sum_score_prepan",
                         data_set = "dat.prepan")
kable(ocir_prepan_model1a_explan_estimates)
ocir_prepan_model1a_explan_estimates

@@

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
```{r ocir model1b sum_score prepan}
# Regression coefficients
ocir_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "ocir.sum_score_base",
                         explan_var = "ocir.sum_score_prepan",
                         data_set = "dat.prepan")
kable(ocir_prepan_model1b_explan_estimates)
ocir_prepan_model1b_explan_estimates

@@

### Model 1a: Disorder hierarchical, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
```{r ocir model1a diff_score retro}
# Regression coefficients
ocir_retro_model1a_estimates <- model1a.estimates(outcome = "ocir.diff_score_base_retro",
                                                 data_set = "dat.retro")
kable(ocir_retro_model1a_estimates)
ocir_retro_model1a_estimates

@@

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
```{r ocir model1b diff_score retro}
# Regression coefficients
ocir_retro_model1b_estimates <- model1b.estimates(outcome = "ocir.diff_score_base_retro",
                                                 data_set = "dat.retro")
kable(ocir_retro_model1b_estimates)
ocir_retro_model1b_estimates

@@

### Model 1a: Disorder hierarchical, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
```{r ocir model1a sum_score retro}
# Regression coefficients
ocir_retro_model1a_explan_estimates <- model1a.explan.estimates(outcome = "ocir.sum_score_base",
                                                               explan_var = "ocir.sum_score_retro",
                                                               data_set = "dat.retro")
kable(ocir_retro_model1a_explan_estimates)
ocir_retro_model1a_explan_estimates

@@

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
```{r ocir model1b sum_score retro}
# Regression coefficients
ocir_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "ocir.sum_score_base",
                                                               explan_var = "ocir.sum_score_retro",
                                                               data_set = "dat.retro")
kable(ocir_retro_model1b_explan_estimates)
ocir_retro_model1b_explan_estimates

@@

### Model 1a: Disorder hierarchical, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
```{r ocir model1a diff_score retro (sensitivity analyses)}
# Regression coefficients
ocir_retro_model1a_estimates <- model1a.estimates(outcome = "ocir.diff_score_base_retro",
                                                 data_set = "dat.retro_sensitivity")
kable(ocir_retro_model1a_estimates)
ocir_retro_model1a_estimates

@@

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
```{r ocir model1b diff_score retro (sensitivity analyses)}
# Regression coefficients
ocir_retro_model1b_estimates <- model1b.estimates(outcome = "ocir.diff_score_base_retro",
                                                 data_set = "dat.retro_sensitivity")
kable(ocir_retro_model1b_estimates)
ocir_retro_model1b_estimates

@@

### Model 1a: Disorder hierarchical, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
```{r ocir model1a sum_score retro (sensitivity analyses)}
# Regression coefficients
ocir_retro_model1a_explan_estimates <- model1a.explan.estimates(outcome = "ocir.sum_score_base",
                                                               explan_var = "ocir.sum_score_retro",
                                                               data_set = "dat.retro_sensitivity")
kable(ocir_retro_model1a_explan_estimates)
ocir_retro_model1a_explan_estimates

@@

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
```{r ocir model1b sum_score retro (sensitivity analyses)}
# Regression coefficients
ocir_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "ocir.sum_score_base",
                                                               explan_var = "ocir.sum_score_retro",
                                                               data_set = "dat.retro_sensitivity")
kable(ocir_retro_model1b_explan_estimates)
ocir_retro_model1b_explan_estimates

@@

### Model 1a: Disorder hierarchical, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
```{r pcl model1a absolute whole sample}
# Regression coefficients
pcl_baseline_model1a_estimates <- model1a.estimates(outcome = "pcl.sum_score_base",
                                                 data_set = "dat")
kable(pcl_baseline_model1a_estimates)
pcl_baseline_model1a_estimates

@@

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
```{r pcl model1b absolute whole sample}
# Regression coefficients
pcl_baseline_model1b_estimates <- model1b.estimates(outcome = "pcl.sum_score_base",
                                                 data_set = "dat")
kable(pcl_baseline_model1b_estimates)
pcl_baseline_model1b_estimates

@@

### Model 1a: Disorder hierarchical, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
```{r pcl model1a diff_score prepan}
# Regression coefficients
pcl_prepan_model1a_estimates <- model1a.estimates(outcome = "pcl.diff_score_base_prepan",
                  data_set = "dat.prepan")
kable(pcl_prepan_model1a_estimates)
pcl_prepan_model1a_estimates

@@

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
```{r pcl model1b diff_score prepan}
# Regression coefficients
pcl_prepan_model1b_estimates <- model1b.estimates(outcome = "pcl.diff_score_base_prepan",
                  data_set = "dat.prepan")
kable(pcl_prepan_model1b_estimates)
pcl_prepan_model1b_estimates

@@

### Model 1a: Disorder hierarchical, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
```{r pcl model1a sum_score prepan}
# Regression coefficients
pcl_prepan_model1a_explan_estimates <- model1a.explan.estimates(outcome = "pcl.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan")
kable(pcl_prepan_model1a_explan_estimates)
pcl_prepan_model1a_explan_estimates

@@

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
```{r pcl model1b sum_score prepan}
# Regression coefficients
pcl_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "pcl.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan")
kable(pcl_prepan_model1b_explan_estimates)
pcl_prepan_model1b_explan_estimates

@@

# SENSITIVITY based on highest level of education

# GAD prepan
## Regression: Absolute scores

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r gad education sensitivity model1b sum_score prepan}
# Regression coefficients
gad_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
                         explan_var = "highest_education_numeric",
                         data_set = "dat.prepan")
kable(gad_prepan_model1b_education_estimates)
gad_prepan_model1b_education_estimates

# Regression diagnostic statistics
gad_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
                         explan_var = "highest_education_numeric",
                         data_set = "dat.prepan")
kable(gad_prepan_model1b_education_reg_stats)
gad_prepan_model1b_education_reg_stats
```

# PHQ prepan
## Regression: Absolute scores

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r phq education sensitivity model1b sum_score prepan}
# Regression coefficients
phq_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
                         explan_var = "highest_education_numeric",
                         data_set = "dat.prepan")
kable(phq_prepan_model1b_education_estimates)
phq_prepan_model1b_education_estimates

# Regression diagnostic statistics
phq_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
                         explan_var = "highest_education_numeric",
                         data_set = "dat.prepan")
kable(phq_prepan_model1b_education_reg_stats)
phq_prepan_model1b_education_reg_stats
```

# OCIR prepan 
## Regression: Absolute scores

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r ocir education sensitivity model1b sum_score prepan}
# Regression coefficients
ocir_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "ocir.sum_score_base",
                         explan_var = "highest_education_numeric",
                         data_set = "dat.prepan")
kable(ocir_prepan_model1b_education_estimates)
ocir_prepan_model1b_education_estimates

# Regression diagnostic statistics
ocir_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "ocir.sum_score_base",
                         explan_var = "highest_education_numeric",
                         data_set = "dat.prepan")
kable(ocir_prepan_model1b_education_reg_stats)
ocir_prepan_model1b_education_reg_stats
```

#PCL prepan 
## Regression: Absolute scores

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r pcl education sensitivty model1b sum_score prepan}
# Regression coefficients
pcl_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "pcl.sum_score_base",
                         explan_var = "highest_education_numeric",
                         data_set = "dat.prepan")
kable(pcl_prepan_model1b_education_estimates)
pcl_prepan_model1b_education_estimates

# Regression diagnostic statistics
pcl_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "pcl.sum_score_base",
                         explan_var = "highest_education_numeric",
                         data_set = "dat.prepan")
kable(pcl_prepan_model1b_education_reg_stats)
pcl_prepan_model1b_education_reg_stats
```

# SENSITIVITY based on employment status

# GAD prepan
## Regression: Absolute scores

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r gad employment sensitivity model1b sum_score prepan}
# Regression coefficients
gad_prepan_model1b_employment_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
                         explan_var = "employment.unemployed_numeric",
                         data_set = "dat.prepan")
kable(gad_prepan_model1b_employment_estimates)
gad_prepan_model1b_employment_estimates

# Regression diagnostic statistics
gad_prepan_model1b_employment_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
                         explan_var = "employment.unemployed_numeric",
                         data_set = "dat.prepan")
kable(gad_prepan_model1b_employment_reg_stats)
gad_prepan_model1b_employment_reg_stats
```

# PHQ prepan
## Regression: Absolute scores

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r phq employment sensitivity model1b sum_score prepan}
# Regression coefficients
phq_prepan_model1b_employment_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
                         explan_var = "employment.unemployed_numeric",
                         data_set = "dat.prepan")
kable(phq_prepan_model1b_employment_estimates)
phq_prepan_model1b_employment_estimates

# Regression diagnostic statistics
phq_prepan_model1b_employment_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
                         explan_var = "employment.unemployed_numeric",
                         data_set = "dat.prepan")
kable(phq_prepan_model1b_employment_reg_stats)
phq_prepan_model1b_employment_reg_stats
```

# OCIR prepan 
## Regression: Absolute scores
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r ocir employment sensitivity model1b sum_score prepan}
# Regression coefficients
ocir_prepan_model1b_employment_estimates <- model1b.explan.estimates(outcome = "ocir.sum_score_base",
                         explan_var = "employment.unemployed_numeric",
                         data_set = "dat.prepan")
kable(ocir_prepan_model1b_employment_estimates)
ocir_prepan_model1b_employment_estimates

# Regression diagnostic statistics
ocir_prepan_model1b_employment_reg_stats <- model1b.explan.reg.stats(outcome = "ocir.sum_score_base",
                         explan_var = "employment.unemployed_numeric",
                         data_set = "dat.prepan")
kable(ocir_prepan_model1b_employment_reg_stats)
ocir_prepan_model1b_employment_reg_stats
```

#PCL prepan 
## Regression: Absolute scores

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r pcl employment sensitivty model1b sum_score prepan}
# Regression coefficients
pcl_prepan_model1b_employment_estimates <- model1b.explan.estimates(outcome = "pcl.sum_score_base",
                         explan_var = "employment.unemployed_numeric",
                         data_set = "dat.prepan")
kable(pcl_prepan_model1b_employment_estimates)
pcl_prepan_model1b_employment_estimates

>>>>

---
title: "PANCHANGE_analysis"
author: "Katherine N Thompson, Christopher Hüebel, Molly R Davies, Kirstin L Purves"
date: Sys.Date()
output:
  html_document:
    df_print: paged
    toc: yes
    toc_depth: 2
    toc_float:
      collapsed: false
    number_sections: false
    highlight: monochrome
    theme: cerulean
code_folding: show

@@

```{r source file path}
#source data directory: data_path
source("../PANCHANGE_raw_path.R")
```

@@

# GAD baseline, not controlling for prior symptoms
### Model 0a: Disorder_hierarchical, Unadjusted
```{r gad model0a absolute whole sample}
# Regression coefficients
gad_baseline_model0a_estimates <- model0a.estimates(outcome = "gad.sum_score_base",
                                                 data_set = "dat")
kable(gad_baseline_model0a_estimates)
gad_baseline_model0a_estimates

# Regression diagnostic statistics
gad_baseline_model0a_reg_stats <- model0a.reg.stats(outcome = "gad.sum_score_base",
                                                 data_set = "dat")
kable(gad_baseline_model0a_reg_stats)
gad_baseline_model0a_reg_stats
```

@@

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r ocir model1b absolute whole sample}
# Regression coefficients
ocir_baseline_model1b_estimates <- model1b.estimates(outcome = "ocir.sum_score_base",
                                                 data_set = "dat")
kable(ocir_baseline_model1b_estimates)
ocir_baseline_model1b_estimates

@@

### Model 1a: Disorder hierarchical, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r ocir model1a diff_score prepan}
# Regression coefficients
ocir_prepan_model1a_estimates <- model1a.estimates(outcome = "ocir.diff_score_base_prepan",
                  data_set = "dat.prepan")
kable(ocir_prepan_model1a_estimates)
ocir_prepan_model1a_estimates

@@

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r ocir model1b diff_score prepan}
# Regression coefficients
ocir_prepan_model1b_estimates <- model1b.estimates(outcome = "ocir.diff_score_base_prepan",
                  data_set = "dat.prepan")
kable(ocir_prepan_model1b_estimates)
ocir_prepan_model1b_estimates

@@

### Model 1a: Disorder hierarchical, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r ocir model1a sum_score prepan}
# Regression coefficients
ocir_prepan_model1a_explan_estimates <- model1a.explan.estimates(outcome = "ocir.sum_score_base",
                         explan_var = "ocir.sum_score_prepan",
                         data_set = "dat.prepan")
kable(ocir_prepan_model1a_explan_estimates)
ocir_prepan_model1a_explan_estimates

@@

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r ocir model1b sum_score prepan}
# Regression coefficients
ocir_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "ocir.sum_score_base",
                         explan_var = "ocir.sum_score_prepan",
                         data_set = "dat.prepan")
kable(ocir_prepan_model1b_explan_estimates)
ocir_prepan_model1b_explan_estimates

@@

### Model 1a: Disorder hierarchical, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r ocir model1a diff_score retro}
# Regression coefficients
ocir_retro_model1a_estimates <- model1a.estimates(outcome = "ocir.diff_score_base_retro",
                                                 data_set = "dat.retro")
kable(ocir_retro_model1a_estimates)
ocir_retro_model1a_estimates

@@

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r ocir model1b diff_score retro}
# Regression coefficients
ocir_retro_model1b_estimates <- model1b.estimates(outcome = "ocir.diff_score_base_retro",
                                                 data_set = "dat.retro")
kable(ocir_retro_model1b_estimates)
ocir_retro_model1b_estimates

@@

### Model 1a: Disorder hierarchical, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r ocir model1a sum_score retro}
# Regression coefficients
ocir_retro_model1a_explan_estimates <- model1a.explan.estimates(outcome = "ocir.sum_score_base",
                                                               explan_var = "ocir.sum_score_retro",
                                                               data_set = "dat.retro")
kable(ocir_retro_model1a_explan_estimates)
ocir_retro_model1a_explan_estimates

@@

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r ocir model1b sum_score retro}
# Regression coefficients
ocir_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "ocir.sum_score_base",
                                                               explan_var = "ocir.sum_score_retro",
                                                               data_set = "dat.retro")
kable(ocir_retro_model1b_explan_estimates)
ocir_retro_model1b_explan_estimates

@@

### Model 1a: Disorder hierarchical, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r ocir model1a diff_score retro (sensitivity analyses)}
# Regression coefficients
ocir_retro_model1a_estimates <- model1a.estimates(outcome = "ocir.diff_score_base_retro",
                                                 data_set = "dat.retro_sensitivity")
kable(ocir_retro_model1a_estimates)
ocir_retro_model1a_estimates

@@

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r ocir model1b diff_score retro (sensitivity analyses)}
# Regression coefficients
ocir_retro_model1b_estimates <- model1b.estimates(outcome = "ocir.diff_score_base_retro",
                                                 data_set = "dat.retro_sensitivity")
kable(ocir_retro_model1b_estimates)
ocir_retro_model1b_estimates

@@

### Model 1a: Disorder hierarchical, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r ocir model1a sum_score retro (sensitivity analyses)}
# Regression coefficients
ocir_retro_model1a_explan_estimates <- model1a.explan.estimates(outcome = "ocir.sum_score_base",
                                                               explan_var = "ocir.sum_score_retro",
                                                               data_set = "dat.retro_sensitivity")
kable(ocir_retro_model1a_explan_estimates)
ocir_retro_model1a_explan_estimates

@@

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r ocir model1b sum_score retro (sensitivity analyses)}
# Regression coefficients
ocir_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "ocir.sum_score_base",
                                                               explan_var = "ocir.sum_score_retro",
                                                               data_set = "dat.retro_sensitivity")
kable(ocir_retro_model1b_explan_estimates)
ocir_retro_model1b_explan_estimates

@@

### Model 1a: Disorder hierarchical, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r pcl model1a absolute whole sample}
# Regression coefficients
pcl_baseline_model1a_estimates <- model1a.estimates(outcome = "pcl.sum_score_base",
                                                 data_set = "dat")
kable(pcl_baseline_model1a_estimates)
pcl_baseline_model1a_estimates

@@

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r pcl model1b absolute whole sample}
# Regression coefficients
pcl_baseline_model1b_estimates <- model1b.estimates(outcome = "pcl.sum_score_base",
                                                 data_set = "dat")
kable(pcl_baseline_model1b_estimates)
pcl_baseline_model1b_estimates

@@

### Model 1a: Disorder hierarchical, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r pcl model1a diff_score prepan}
# Regression coefficients
pcl_prepan_model1a_estimates <- model1a.estimates(outcome = "pcl.diff_score_base_prepan",
                  data_set = "dat.prepan")
kable(pcl_prepan_model1a_estimates)
pcl_prepan_model1a_estimates

@@

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r pcl model1b diff_score prepan}
# Regression coefficients
pcl_prepan_model1b_estimates <- model1b.estimates(outcome = "pcl.diff_score_base_prepan",
                  data_set = "dat.prepan")
kable(pcl_prepan_model1b_estimates)
pcl_prepan_model1b_estimates

@@

### Model 1a: Disorder hierarchical, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r pcl model1a sum_score prepan}
# Regression coefficients
pcl_prepan_model1a_explan_estimates <- model1a.explan.estimates(outcome = "pcl.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan")
kable(pcl_prepan_model1a_explan_estimates)
pcl_prepan_model1a_explan_estimates

@@

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r pcl model1b sum_score prepan}
# Regression coefficients
pcl_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "pcl.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan")
kable(pcl_prepan_model1b_explan_estimates)
pcl_prepan_model1b_explan_estimates

@@

# Sensitivity based on highest level of education 
# Function change to include highest education as predictor

```{r model1b education function}
model1b.estimates <- function(outcome, data_set) {
  # define the variable name of the dependent variable
  dependent.variable <- outcome
  # define the independent variables
  independent.variables <- c("depression_and_anxiety",
                             "eating_disorders",
                             "obsessive_compulsive_disorders",
                             "bipolar_and_schizophrenia",
                             "mhd.posttraumatic_stress_disorder_ptsd",
                             "autism_spectrum_disorder",
                             "mhd.attention_deficit_hyperactivity_disorder",
                             "mhd.personality_disorder",
                             "Gender_collapsed",
                             "age_category_collapsed",
                             "Ethnicity_collapsed",
                             "key_worker",
                             "time_diff_coping_lockdown_march_23", 
                             "highest_education"
                                )
  # create the formula
  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
  glm.formula
               "age_category_collapsed19-25" = "19-25 years",
               "age_category_collapsed26-35" = "26-35 years",
               "age_category_collapsed36-45" = "36-45 years",
               "age_category_collapsed46-55" = "46-55 years",
               "age_category_collapsed56-65" = "56-65 years",
               "age_category_collapsed66-70" = "66-70 years",
               "age_category_collapsed71-75" = "71-75 years",
               "age_category_collapsed76+" = "76+ years",
               "time_diff_coping_lockdown_march_23" = "Time difference: Lockdown to baseline", 
               "highest_educationNVQ" = "Highest education NVQ", 
               "highest_educationA-levels" = "Highest education A-Levels",
               "highest_educationUniversity" = "Highest education University"

```{r model1b.explan education function}
model1b.explan.estimates <- function(outcome, explan_var, data_set) {
  # define the variable name of the dependent variable
  dependent.variable <- outcome
  # define the independent variables
  independent.variables <- c(explan_var,
                             "depression_and_anxiety",
                             "eating_disorders",
                             "obsessive_compulsive_disorders",
                             "bipolar_and_schizophrenia",
                             "mhd.posttraumatic_stress_disorder_ptsd",
                             "autism_spectrum_disorder",
                             "mhd.attention_deficit_hyperactivity_disorder",
                             "mhd.personality_disorder",
                             "Gender_collapsed",
                             "age_category_collapsed",
                             "Ethnicity_collapsed",
                             "key_worker",
                             "time_diff_coping_lockdown_march_23", 
                             "highest_education"
  )
  # create the formula
  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
  glm.formula
               "age_category_collapsed19-25" = "19-25 years",
               "age_category_collapsed26-35" = "26-35 years",
               "age_category_collapsed36-45" = "36-45 years",
               "age_category_collapsed46-55" = "46-55 years",
               "age_category_collapsed56-65" = "56-65 years",
               "age_category_collapsed66-70" = "66-70 years",
               "age_category_collapsed71-75" = "71-75 years",
               "age_category_collapsed76+" = "76+ years",
               "time_diff_coping_lockdown_march_23" = "Time difference: Lockdown to baseline", 
               "highest_educationNVQ" = "Highest education NVQ", 
               "highest_educationA-levels" = "Highest education A-Levels",
               "highest_educationUniversity" = "Highest education University"

# GAD prepan
## Regression: Absolute scores
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r gad education sensitivity model1b sum_score prepan}
# Regression coefficients
gad_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan")
kable(gad_prepan_model1b_education_estimates)
gad_prepan_model1b_education_estimates

# Regression diagnostic statistics
gad_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan")
kable(gad_prepan_model1b_education_reg_stats)
gad_prepan_model1b_education_reg_stats
```

# PHQ prepan
## Regression: Absolute scores
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r phq education sensitivity model1b sum_score prepan}
# Regression coefficients
phq_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan")
kable(phq_prepan_model1b_education_estimates)
phq_prepan_model1b_education_estimates

# Regression diagnostic statistics
phq_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan")
kable(phq_prepan_model1b_education_reg_stats)
phq_prepan_model1b_education_reg_stats
```

# OCIR prepan 
## Regression: Absolute scores
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r ocir education sensitivity model1b sum_score prepan}
# Regression coefficients
ocir_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "ocir.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan")
kable(ocir_prepan_model1b_education_estimates)
ocir_prepan_model1b_education_estimates

# Regression diagnostic statistics
ocir_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "ocir.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan")
kable(ocir_prepan_model1b_education_reg_stats)
ocir_prepan_model1b_education_reg_stats
```

#PCL prepan 
## Regression: Absolute scores
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r pcl education sensitivty model1b sum_score prepan}
# Regression coefficients
pcl_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "pcl.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan")
kable(pcl_prepan_model1b_education_estimates)
pcl_prepan_model1b_education_estimates

# Regression diagnostic statistics
pcl_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "pcl.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan")
kable(pcl_prepan_model1b_education_reg_stats)
pcl_prepan_model1b_education_reg_stats
```

# Sensitivity anlayses based on employment prior to covid
# Function change to include employment prior to covid as predictors
